Reasoning About a Capability Machine with Local Capabilities

### 2017-09-29 esop-2018/paper.tex
typo

\emph{Arguments and local capabilities} 
%Stack and return pointer
%Local capabilities cannot be "freely used"
%Safety dictated by LR
%Need to dynamical check whether we overwrite our local stuff.
Local capabilities are a central part of the calling convention as they are used
to construct stack and return pointers. The use of local capabilities for the
calling convention unfortunately limits the extent to which local capabilities
can be used for other things. Say we are using the calling convention and
receive a local capability other than the stack and return pointer, then we need
to be careful if we want to use it because it may be an alias to the stack
pointer. That is, if we first push something to the stack and then write to the
local capability, then we may be (tricked into) overwriting our own local state.
The logical relation helps by telling us what we need to ascertain or check in
such scenarios to guarantee safety and preserve our invariants, but such checks
may be costly and it is not clear to us whether there are practical scenario's
where this might be realistic.

>>>>

\emph{Arguments and local capabilities} 
%Stack and return pointer
%Local capabilities cannot be "freely used"
%Safety dictated by LR
%Need to dynamical check whether we overwrite our local stuff.
Local capabilities are a central part of the calling convention as they are used
to construct stack and return pointers. The use of local capabilities for the
calling convention unfortunately limits the extent to which local capabilities
can be used for other things. Say we are using the calling convention and
receive a local capability other than the stack and return pointer, then we need
to be careful if we want to use it because it may be an alias to the stack
pointer. That is, if we first push something to the stack and then write to the
local capability, then we may be (tricked into) overwriting our own local state.
The logical relation helps by telling us what we need to ascertain or check in
such scenarios to guarantee safety and preserve our invariants, but such checks
may be costly and it is not clear to us whether there are practical scenarios
where this might be realistic.
